Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-16 doc/journal/fpgapaperfinal/FPGAPaper/partitioning.tex
Adding feng rent's rule reference
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4549 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

\begin{equation}
\forall i, \abs*{ \frac{| P1_i |}{|P1_i \cup P2_i |} - 0.5} < unbalance
\end{equation}
where $P1_i$ denotes the set of all blocks of type $i$ in partition 1.

@@

On average, the best minimum channel width was obtained when constraining both packing and placement. However, constraining packing alone performed significantly better than constraining placement alone. This shows that the VPR packer strongly benefits from partitioning constraints when targeting an interposer-based architecture, likely because it forbids the packing of primitives that are not naturally related into one function block. Interestingly, other recent work targeting conventional FPGAs has shown that using a partitioner to guide packing benefits routability [Wenyi Feng, et al, “Rent’s Rule Based Packing for Routability Optimization,” FPGA 2014 ]. On the other hand, The VPR placement algorithm with the enhancements described in Section 4 sees only a modest routability benefit from the partitioning constraints.

>>>>

\begin{equation}
\forall i, \abs*{ \frac{| P1_i |}{|P1_i \cup P2_i |} - 0.5} < unbalance
\end{equation}
where $P1_i$ is the set of all blocks of type $i$ in partition 1.

@@

On average, the best minimum channel width was obtained when constraining both packing and placement. However, constraining packing alone performed significantly better than constraining placement alone. This shows that the VPR packer strongly benefits from partitioning constraints when targeting an interposer-based architecture, likely because it forbids the packing of primitives that are not naturally related into one function block. Interestingly, other recent work targeting conventional FPGAs has shown that using a partitioner to guide packing benefits routability\cite{feng2014rent}. On the other hand, The VPR placement algorithm with the enhancements described in Section 4 sees only a modest routability benefit from the partitioning constraints.
